;;
;; Domain:     latexformat.com
;; Exported:   2017-11-03 20:01:34
;;
;; This file is intended for use for informational and archival
;; purposes ONLY and MUST be edited before use on a production
;; DNS server.  In particular, you must:
;;   -- update the SOA record with the correct authoritative name server
;;   -- update the SOA record with the contact e-mail address information
;;   -- update the NS record(s) with the authoritative name servers for this domain.
;;
;; For further information, please consult the BIND documentation
;; located on the following website:
;;
;; http://www.isc.org/
;;
;; And RFC 1035:
;;
;; http://www.ietf.org/rfc/rfc1035.txt
;;
;; Please note that we do NOT offer technical support for any use
;; of this zone data, the BIND name server, or any other third-party
;; DNS software.
;;
;; Use at your own risk.
$ORIGIN .
        @       3600    IN      SOA     latexformat.com.        root.latexformat.com.   (
        2026140589      ; serial
        7200            ; refresh
        3600            ; retry
        86400           ; expire
        3600)           ; minimum



        ;; NS Records (YOU MUST CHANGE THIS)
        latexformat.com.        300     IN      NS      REPLACE&ME$WITH^YOUR@NAMESERVER.

;; MX Records
latexformat.com.        300     IN      MX      1       mail.latexformat.com.


;; CNAME Records
www.latexformat.com.    300     IN      CNAME   latexformat.com.

;; A Records (IPv4 addresses)
mail.latexformat.com.   300     IN      A       72.14.182.116
latexformat.com.        300     IN      A       72.14.182.116

;; AAAA Records (IPv6 addresses)
latexformat.com.        300     IN      AAAA    2600:3c00::f03c:91ff:fe60:ea75
